\large{Vipassana for Hackers} \\ \Huge{Paper Three: Why Meditate?} \\ \large\textit{Version 0.1}

### 2020-03-29 paper-three/paper-three.tex
vipassana vs. blockchain
lucid dreams; service

>>>>

The purpose of various forms of meditation should be understood clearly, as the
intention of techniques can vary wildly from one to the next. Where the purpose of
meditation is simply to relax, it is difficult to say that meditation is more
valuable than a nap. Especially for our chronically sleep-deprived society, it's
unlikely their effects would differ much.

However, most meditation techniques are not intended to relax the meditator. Whatever
the object of a meditation technique (one of the five sense doors, bodily sensation,
or objects of mind) the very act of meditation is one of
